Clicks and Cliques

### 2018-12-23 papersoul.Rnw
from qplot to ggplot in race chunk

ggplot() + 
  geom_path(data = us, aes(long, lat, group=group), color = 'grey' ) +
  geom_point(data=lon.lat, aes(x=lon, y=lat, size = pop100), alpha = .5) +
  xlab('') + ylab('') + 
  scale_size(range = c(5,20)) + 
  scale_color_brewer(type = 'seq') +
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(), 
        legend.position = 'none')
@
\caption{Geographical location of the 26 communities in the data, dot's size represents population. Only two communities on the west coast are included. \label{map}}
\end{figure}

@@

aux <- soul$QD111
levels(aux)[c(4,6:10,15:17,19,20) ] <- 'Other'
levels(aux)[c(1,2,5,7,8,10) ] <- 'Non Response'
levels(aux)[2] <- 'Hispanic'
aux[soul$QD10=='Yes'] <- 'Hispanic'
soul$race  <- factor(aux)

@@

qplot(data=tab, diver,logit(statistic.CCEGRP2Attached),size=I(5)) + theme(axis.text.y = element_text( size=I(10)) ) + ylab('Proportion of Attach (logit scale)') + xlab('Race diversity index') + geom_smooth(se=FALSE, method='lm', size=I(1))

>>>>

ggplot() + 
  geom_path(data = us, aes(long, lat, group = group), color = 'grey' ) +
  geom_point(data = lon.lat, aes(x = lon, y = lat, size = pop100), alpha = .5) +
  xlab('') + ylab('') + 
  scale_size(range = c(5,20)) + 
  scale_color_brewer(type = 'seq') +
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(), 
        legend.position = 'none')
@
\caption{Geographical location of the 26 communities in the data, dot's size represents population. Only two communities on the west coast are included. \label{map}}
\end{figure}

@@

aux <- soul$QD111

levels(aux)[c(4,6:10,15:17,19,20) ] <- 'Other'
levels(aux)[c(1,2,5,7,8,10) ] <- 'Non Response'
levels(aux)[2] <- 'Hispanic'
aux[soul$QD10 == 'Yes'] <- 'Hispanic'
soul$race  <- factor(aux)

@@

ggplot(data = tab, aes(x = diver, y = logit(statistic.CCEGRP2Attached))) + geom_point(size = I(5)) + theme(axis.text.y = element_text( size = I(10)) ) + labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index') + geom_smooth(se = FALSE, method = 'lm', size = I(1))
